### 2021-12-21 README.Rmd

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Northern Pikeminnow Abundance in Deadwater Slough and Potential Impacts to Local Chinook Salmon Populations"
Authors <- "Carmichael, Richard A., Kevin E. See, Nick Porter, and Michael W. Ackerman"
yr <- 2021
Journal <- "TBD"

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations in the Upper Salmon River, Idaho"
Authors <- "Ackerman, Michael W., Nicholas J. Porter, Kevin E. See, Michael S. Hall, Tara E. Blackman, and Richard A. Carmichael, and Michael W. Ackerman"
yr <- 2022
Journal <- "Transactions of the American Fisheries Society"

@@

  - [:file\_folder: data](/analysis/data): Relevant data used in study analyses.
  - [:file\_folder: figures](/analysis/figures): Figures, plots, and other
    illustrations.
  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file).
  - [:file\_folder: supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including photographs, related R scripts, and files associated with the bioenergetics analysis.
  - [:file\_folder: templates](/analysis/bioenergetics): Some files used to format the manuscript.
